General constraints on magic distillation protocols from statistical mechanics

### 2021-05-07 notes/notes.tex
some quick fixes
No numerics yet. Corrected and tidied all appendices and outlook, answered all blue comments

\ddd{[Going forward:
\begin{enumerate}
\item Does the ``last elbow'' give the same bound? Is it as simple?
\item Numerically is this about as good as it gets from majorisation?
\item How does this rate compare with existing literature?
\end{enumerate}}

@@

@@

>>>>

@@

With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed positive integer $n$ and probability $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(m; n, p) \geq \sum\limits_{\ell=0}^{m/2}\left[ 16\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
		&\hspace{14pt} \text{for all even } m\in [2,n] \\
		&\text{2. } \Phi_+(m; n, p) \leq \sum\limits_{\ell=0}^{m/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{n}}{p}}, \\
		&\hspace{14pt} \text{for all even } a\in [2,n] \\
		&\text{3. } \Phi_-(m; n, p) \geq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd }a\in [1,n] \\
		&\text{4. } \Phi_-(m; n, p) \leq \sum\limits_{\ell=1}^{(m-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{n}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{n}}{p}},\ \text{for all odd } a\in [1,n]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

\subsection{Deriving distillation bounds from the last elbow}
\label{sec:last_elb}

\nick{RESTRUCTURE}

To find the coordinates of the \textbf{last} elbow $(x_E, L_E)$, where $E$ is the number of elbows, we need to evaluate the minimum rescaled component,
\begin{align}
	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} \coloneqq (3\Z)^{n}\times \nonumber\\
	&\min\limits_{i,j,k}\Big\{ (-v)^{n-\alpha} u^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta ( i E_0 + j E_1 + k E_2 )} \Big\}, \label{eq:min_slope}
\end{align}
where $0 \leq i,j,k \leq n$ and $\alpha \coloneqq i+j+k \leq n$.
Notice that for $0 \leq \epsilon \leq 3/7$, we have $v \geq u$. 
We need the sum $\alpha = i+j+k$ to be odd for the expression to be negative.

Given an odd value for the sum $\alpha$, the term $v^{n-\alpha} u^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed (and negative), so the expression is minimised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} = \nonumber\\
	&-(3\Z)^{n} v^n e^{n\beta E_0}\max\limits_{\substack{\alpha = 1,3, \\ \dots,n-1}}{\Big\{ \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}.
\end{align}
If the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ then the minimum occurs at $\alpha=1$, otherwise it occurs at $\alpha = n-1$.

The minimum rescaled component can then be expressed as
\begin{equation}
\bmw(\rho_{\rm{S}} | \sigma)_{\rm{min}} =
	\begin{cases}
		-(3\Z)^{n} v^{n-1} u e^{\beta [(n-1)E_0 + E_{\rm{max}}]}, &\epsilon \leq \epsilon_{\star},\ \hspace{3pt}\rm{(C1)}	\\
		-(3\Z)^{n} v u^{n-1} e^{\beta [E_0 + (n-1)E_{\rm{max}}]}, &\epsilon > \epsilon_{\star}.\ \hspace{5pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case $\rm{(C1)}$ can correspond to $(i,j,k) = (1,0,0)$ if $E_{\rm{max}} = E_0$, when the multiplicity is $m_{100} = 2n$ and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{100}, \bmw(\sigma)_{100}$ or it can correspond to $(i,j,k) = (0,1,0)$ ($(i,j,k) = (0,0,1)$), if $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{010} = 3n$ ($m_{001} = 3n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{010}, \bmw(\sigma)_{010}$ ($\bmw(\rho_{\rm{S}})_{001}, \bmw(\sigma)_{001}$).
Case $\rm{(C2)}$ corresponds to $(i,j,k) = (0,n-1,0)$ ($(i,j,k) = (0,0,n-1)$)
if we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), when the multiplicity is $m_{0,n-1,0} = 3^{n-1}n$ ($m_{0,0,n-1} = 3^{n-1}n$) and the corresponding Wigner components are $\bmw(\rho_{\rm{S}})_{0,n-1,0}, \bmw(\sigma)_{0,n-1,0}$ ($\bmw(\rho_{\rm{S}})_{0,0,n-1}, \bmw(\sigma)_{0,0,n-1}$).

The last elbow coordinates can finally be derived by sutracting the appropriate rescaled component from 1, $(x_E, L_E) =$
\begin{equation}\label{eq:last_elb_coords}
	\begin{cases}
		&\left( 1-\dfrac{2n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 2n v^{n-1} u \right), \vspace{5pt}\\
		&\hspace{5pt} \text{if } E_{\rm{max}} = E_0, \hspace{51pt}\rm{(C1a)} \vspace{10pt}\\
		&\left( 1-\dfrac{3n}{(3\Z_\beta)^n}e^{-\beta [(n-1)E_0 + E_{\rm{max}}]},\ 1 + 3n v^{n-1} u \right), \vspace{5pt}\\
		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \leq \epsilon_{\star}, \hspace{20pt}\rm{(C1b)} \vspace{10pt}\\
		&\left( 1-\dfrac{n}{3\Z_\beta^n}e^{-\beta [E_0 + (n-1)E_{\rm{max}}]},\ 1 + 3^{n-1}n v u^{n-1} \right), \vspace{5pt}\\
		&\hspace{5pt} \text{if } E_{\rm{max}} > E_0, \epsilon \geq \epsilon_{\star}. \hspace{22pt}\rm{(C2)}
	\end{cases}
\end{equation}

Assuming that $E_{\rm{max}} > E_0$ for clarity, we have the same three scenarios as in the case of the first elbow bound:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' < \epsilon  \leq \epsilon_{\star}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $\beta < \beta_{\star}$ and $\epsilon' \leq \epsilon_{\star} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $\beta < \beta_{\star}$ and $\epsilon_{\star} \leq \epsilon' < \epsilon$ or $\beta \geq \beta_{\star}$.
\end{enumerate}
Now using last elbow constraint, derived in~\cref{app:elb_constraints}, we can calculate new distillation bounds.
The last elbow bounds can be rephrased in terms of the first elbow bound, leading to $R_{\rm{last-elb}} - R_{\rm{first-elb}} = $
\begin{equation}\label{eq:last_elb_coords}
	\begin{cases}
		\dfrac{1}{n} \dfrac{\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C1)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon)v(\epsilon')}{u(\epsilon)u(\epsilon')}} - 2\beta(E_{\rm{max}} - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C1)}, \vspace{10pt}\\
		\dfrac{1}{n} \dfrac{\log{\frac{v(\epsilon')u(\epsilon')}{v(\epsilon')u(\epsilon)}}}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F(\beta))},\ &\rm{(C2)} \rightarrow \rm{(C2)}, 
	\end{cases}
\end{equation}

Note that the last elbow bounds have a dependence on $n$, which interestingly is due to $n$ being even.
Had we considered \textbf{odd} number of copies $n$, then the first elbow bound would depend on $n$ and the last elbow bound would not.
This, along with the unital fragment analysis, makes me think that calculating the bounds again for odd $n$ or $\epsilon > 3/7$ would reveal nice symmetries of the analysis, but it's probably not worth the time, so including last elbow analysis properly feels incomplete.

Determining the sign of the difference between the last and first elbow bounds tells us which bound is better.
The term $\log{\frac{u(\epsilon)v(\epsilon')}{u(\epsilon')v(\epsilon)}}$ is always positive for $\epsilon > \epsilon'$, therefore the last elbow bound, compared to the first elbow bound, is always \textbf{worse} in the first scenario and always \textbf{better} in the third scenario (remember, this is the yellow-ish right part of~\cref{fig:rate_contour}).

In the second scenario ($\rm{(C2)} \rightarrow \rm{(C1)}$), the expression looks very weird to me, seems like the difference tends to $-\infty$ as $E_{\rm{max}} \rightarrow \infty$.
I am a bit stuck with this expression and I am not sure it's worth putting more time in it.
